--- 
title: "README"
output: 
  md_document:
  variant: markdown_github

params:
  NVIpkg: "NVIcheckmate"
---

```{r, include = FALSE}
NVIpkg <- params$NVIpkg
NVIpkg_inline <- paste0("`", NVIpkg, "`")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`r paste0(NVIpkg, ": ", desc::desc_get_field(key = "Title"))`
================

<!-- README.md is generated from README.Rmd. Please edit that file -->

  - [Overview](#overview)
  - [Installation](#installation)
  - [Usage](#usage)
  - [Copyright and license](#copyright-and-license)
  - [Contributing](#contributing)

# Overview
`NVIcheckmate` extends [`checkmate`](https://CRAN.R-project.org/package=checkmate)
with functions for argument checking that are adapted for NVIverse.

```{r, include = FALSE}
description <- desc::desc_get_field(key = "Description")
```

```{r child=system.file('templates', "README_NVIverse.Rmd", package = "NVIpackager")}
```

The main purpose of `NVIcheckmate` is to provide checks and assertions for functions 
in `NVIverse` in the case that the checks and assertions are not available in `checkmate`. 
These include specialized argument checking as well as checking other requirements 
like if a package is installed, if the users credentials are available and, if an 
valid ODBC-channel exists.

In addition, an argument for adding a custom message is included in selected assertions 
from `checkmate`. Thereby, the error messages for a specific function may be explained 
to provide more meaningful error messages.

`NVIcheckmate` is intended for use together with `checkmate`. `NVIcheckmate` intend 
to follow the same principles as `checkmate` concerning input and error messages. 
The argument checking in `NVIverse` uses the assert class in `checkmate` for 
collecting and reporting the assertions, and assertions from `checkmate` and 
`NVIcheckmate` are combined when checking the arguments of a function.

When and if functionality covered by `NVIcheckmate` are included in `checkmate` 
as available at Cran, the corresponding function will be depreciated and thereafter 
removed from `NVIcheckmate`. 

# Installation
```{r child=system.file('templates', "README_installation.Rmd", package = "NVIpackager")}
```

# Usage
```{r child=system.file('templates', "README_usage_attach.Rmd", package = "NVIpackager")}
```

`r paste0(NVIpkg_inline, 
   "", 
   sub(substr(description,1,1), tolower(substr(description,1,1)), description))`

```{r child=system.file('templates', "README_usage_help.Rmd", package = "NVIpackager")}
```

# Copyright and license

#### NVIcheckmate
```{r child=system.file('templates', "README_copyright_and_license.Rmd", package = "NVIpackager")}
```
Copyright (c) 2021 Norwegian Veterinary Institute  
License: BSD 3-Clause  
  
Functions and code from `checkmate` have been imported into `NVIcheckmate`. For some of 
them, the code have been partly modified. An overwiew of the functional modifications are 
given in Table 2. In addition, some technical changes like escaping character, changing 
links and correcting typos have been performed. The modifications are listed in the respective 
source files. Code from `checkmate` are the copyright of the copyright holders of `checkmate`.
  
#### checkmate
Copyright (c) 2019 Michael Lang (michellang@@gmail.com)  
License: BSD 3-Clause  
  
#### Table 2. Functions and code imported from `checkmate`

```{r echo = FALSE, results = 'asis'}
imports <- as.data.frame(rbind( c("assert.R", 
                                 "./R",
                                  "Combines multiple checks into one assertion",
                                 "None. Imported as is from checkmate 2.1.0 at Github to include argument 'add'"),
                                c("mstopOrPush",  
                                  "./R",
                                  "Internal function. Located in file assert.R",
                                  "None"),
                                c("mstop",  
                                  "./R",
                                  "Internal function. Located in file helper.R",
                                  "None"),
                               c("makeAssertFunction.R", 
                                 "./R",
                                 "Creates an assertion function from a check function",
                                 "Adds the argument 'comment' when creating an assertion function"),
                               c("assert_names", 
                                 "./R",
                                 "Perform various checks on character vectors, usually names",
                                 "Based on check_names and includes the argument 'comment'"),
                               c("assert_character", 
                                 "./R",
                                 "Check if an argument is a vector of type character",
                                 "Based on check_character and includes the argument 'comment'"),
                               c("assert.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "None"),
                                c("checker.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "Only included information on check_- and assert_-functions, the rest were removed"),
                                c("fmatch.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "None"),
                                c("makeFunction.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "None"),
                                c("na-handling.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "None"),
                                c("null.ok.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "None"),
                                c("sorted.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "None"),
                                c("x.R",  
                                  "./man-roxygen",
                                  "help template",
                                  "None")))
colnames(imports) <- c("Function", "Directory", "Description", "Modification")
knitr::kable(x = imports, col.names = c("Function", "Directory", "Description", "Functional modifications")) 
```

# Contributing
```{r child=system.file('templates', "README_contributing.Rmd", package = "NVIpackager")}
```

<!-- Code of conduct -->
-----
```{r child=system.file('templates', "README_code_of_conduct.Rmd", package = "NVIpackager")}
```
